---
title: "Homework 6"
author: "Jia Ji"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r load_libraries}
library(tidyverse)
library(modelr)
```

### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

## Problem 2

```{r message = FALSE, warning = FALSE}
homicide_df = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with Baltimore, MD.


```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate), 
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error),
    p_val = rstatix::p_format(p.value, digits = 2)) %>% 
  select(term, OR, CI_lower,CI_upper, p_val) %>% 
  mutate(term = str_replace(term, "victim_age", "Victim age"),
         term = str_replace(term, "victim_race", "Victim Race: "),
         term = str_replace(term, "victim_sex", "Victim Sex: ")) %>% 
  knitr::kable(digits = 3, align = "lccc", 
               col.names = c("Term", "Estimated adjusted OR", "CI lower bound", "CI upper bound", "p-value"))
```

For the city of Baltimore, MD, the homicides whose victim is male are significantly less like to be resolved than those whose victim is female.


```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error),
    p_val = rstatix::p_format(p.value, digits = 2)
  ) %>% 
  filter(term == "victim_sexMale") %>% 
  select(city_state, OR, CI_lower,CI_upper, p_val) 
models_results_df %>% 
  knitr::kable(digits = 3, align = "llccc", col.names = c("City", "Estimated adjusted OR", "CI lower bound", "CI upper bound", "p-value"))
```

Here is a plot of estimated ORs and CIs for each city. 


```{r}
models_results_df %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = "City", y = "Estimated OR with CI")
```

It shown that odds ratios are lower than 1 in most cities, indicating that it is less often for homicides in which the victim is male to be resolved by arrest.


